Codebook
========

Variable list and descriptions
------------------------------

Variable name        | Description
---------------------|------------
subject              | Subject ID, ranging from 1 to 30.
activity             | Activity name (WALKING, WALKING_UPSTAIRS, WALKING_DOWNSTAIRS, SITTING, STANDING, LAYING)
feature_Domain       | Time domain or frequency domain signal (Time or Frequency)
feature_Instrument   | Measuring instrument (Accelerometer, Gyroscope)
feature_Acceleration | Acceleration signal (Body or Gravity)
feature_Calc         | Type of calculated data from signals (linear acceleration, angular velocity, linear acceleration Jerk, angular velocity Jerk, linear acceleration magnitude, angular velocity magnitude, linear acceleration Jerk magnitude, angular velocity Jerk magnitude)
feature_Estimation   | Estimation of statistical values (Mean, SD)
feature_Axis         | 3-axial signals in the X, Y and Z directions (X, Y, Z)
count                | Count of data points per group
average              | Average of each variable for each activity and each subject

Dataset structure
-----------------

```{r}
str(dt_tidy)
```

List the key variables in the data table
----------------------------------------

```{r}
key(dt_tidy)
```

Summary of variables
--------------------

```{r}
summary(dt_tidy)
```

Save to file
------------

Save data table objects to a tab-delimited text file called `tidy.txt`.

```{r save}
write.table(dt_tidy, file="./tidy.txt", row.name=FALSE, sep="\t", quote=FALSE)
```